Quantum parallel parallel Markov chain Monte Carlo

### 2021-11-16 main.tex
exponential searching algorithm

\title{A quantum parallel parallel Markov chain Monte Carlo}
\date{}

@@

\begin{algorithm}[t!]
	\caption{Grover's algorithm for quantum search}\label{alg:grover}
	\KwData{An oracle gate $\U_f$ taking $\ket{x}\ket{y}$ to $\ket{x}\ket{y\oplus f(x)}$ for a function $f(x):\{0,\dots,N-1\}\rightarrow \{0,1\}$ that satisfies $f(x_0)=1$ for a single $x_0$; $n+1=\log_2(N)+1$ quantum states initialized to $\ket{0}^{\otimes n} \ket{1}$; an integer $R>\pi\sqrt{N}/4$ denoting the number of Grover iterations.}
	\KwResult{An $n$-bit binary string $x_0$ satisfying $f(x_0)=1$ with error less than $1/N$.}
	$\H^{\otimes n+1}\ket{0}^{\otimes n}\ket{1} \longrightarrow \ket{h}\ket{-}$; \hspace{11.5em} \Comment{\hspace{0.3em}$\ket{h}=\frac{1}{\sqrt{N}} \sum_{x=0}^{N-1} \ket{x}$.} 
	$\ket{h}\ket{-} \longrightarrow \G^R \ket{h}\ket{-} \approx \ket{x_0}\ket{-}$;    \hspace{3em}         \Comment{$\G= \Big(2\ket{h}\bra{h}-\I \Big) \Big( \I - 2 \ket{x_0}\bra{x_0} \Big)$}
	$\ket{x_0} \longrightarrow x_0$\;
	\Return{$x_0$}\ .
\end{algorithm}

@@

>>>>

\title{Quantum parallel parallel Markov chain Monte Carlo}
\date{}

@@

\subsection{Quantum search}

\begin{algorithm}[t!]
	\caption{Quantum search algorithm \citep{grover1996fast}}\label{alg:grover}
	\KwData{An oracle gate $\U_f$ taking $\ket{x}\ket{y}$ to $\ket{x}\ket{y\oplus f(x)}$ for a function $f(x):\{0,\dots,N-1\}\rightarrow \{0,1\}$ that satisfies $f(x_0)=1$ for a single $x_0$; $n+1=\log_2(N)+1$ quantum states initialized to $\ket{0}^{\otimes n} \ket{1}$; an integer $R=\ceil{\pi\sqrt{N}/4}$ denoting the number of Grover iterations.}
	\KwResult{An $n$-bit binary string $x_0$ satisfying $f(x_0)=1$ with error less than $1/N$.}
	$\H^{\otimes n+1}\ket{0}^{\otimes n}\ket{1} \longrightarrow \ket{h}\ket{-}$; \hspace{11.5em} \Comment{\hspace{0.3em}$\ket{h}=\frac{1}{\sqrt{N}} \sum_{x=0}^{N-1} \ket{x}$.} 
	$\ket{h}\ket{-} \longrightarrow \G^R \ket{h}\ket{-} \approx \ket{x_0}\ket{-}$;    \hspace{3em}         \Comment{$\G= \Big(2\ket{h}\bra{h}-\I \Big) \Big( \I - 2 \ket{x_0}\bra{x_0} \Big)$}
	$\ket{x_0} \longrightarrow x_0$\;
	\Return{$x_0$}\ .
\end{algorithm}

@@

 \begin{algorithm}[t!]
 	\caption{Quantum exponential searching algorithm \citep{boyer1998tight}}\label{alg:expoSearch}
 	\KwData{An oracle gate $\U_f$ taking $\ket{x}\ket{y}$ to $\ket{x}\ket{y\oplus f(x)}$ for a function $f(x):\{0,\dots,N-1\}\rightarrow \{0,1\}$ with unknown number of solutions; $n=\log_2(N)$.}
 	\KwResult{An $n$-bit binary string $x_0$ satisfying $f(x_0)=1$.}
 	$m \gets 1$\;
 	$\lambda \gets 6/5$\;
 	success $\gets$ \textcolor{blue}{FALSE}\;
 	\While{\emph{success}$\neq$\emph{\textcolor{blue}{TRUE}}}{
 	$j \gets Uniform \{0,\cdots,m-1\}$\;
 	$\H^{\otimes n+1}\ket{0}^{\otimes n}\ket{1} \longrightarrow \ket{h}\ket{-}$\; 
 	$\ket{h}\ket{-} \longrightarrow \G^j \ket{h}\ket{-} = \ket{x}\ket{-}$;\hspace{1em}  \Comment{$j$ Grover iterations from Alg \ref{alg:grover}.}  
 	$\ket{x} \longrightarrow x$; \hspace{16em} \Comment{Measure and check.}  
 	\uIf{$f(x)=1$}{$x_0 \gets x$\;
 		success $\gets$  \textcolor{blue}{TRUE}\;}
 	\Else{$m \gets \min\left( \lambda m, \sqrt{N}\right)$;\hspace{4em}  \Comment{Increase $m$ in case of failure.}
 }}
 	\Return{$x_0$}
 \end{algorithm}

 \subsection{Quantum minimization}
